Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-11-07 paper/paper-MinD.tex
add SI descriptions to the paper Tested everything on bennet.

>>>>

\section*{Supplementary Information 1}

Movie that shows the evolution of MinD density over a 250 second
interval in a wild-type, pill-shaped cell.  There is one frame for
every half second of simulation time. Above are results from the
stochastic model and below are results from the deterministic model.
The density shown is integrated over the direction normal to the
screen, so that the data is shown in molecules/$\micron^2$.

\section*{Supplementary Information 2}

Movie that shows the evolution of MinD density over a 350 second
interval in the shape A cell.  There is one frame for every half
second of simulation time. Above are results from the stochastic model
and below are results from the deterministic model.  The density shown
is integrated over the direction normal to the screen, so that the
data is shown in molecules/$\micron^2$.

\section*{Supplementary Information 3}

Movie that shows the evolution of MinD density over a 350 second
interval in the shape B cell.  There is one frame for every half
second of simulation time. Above are results from the stochastic model
and below are results from the deterministic model.  The density shown
is integrated over the direction normal to the screen, so that the
data is shown in molecules/$\micron^2$.

\section*{Supplementary Information 4}

Movie that shows the evolution of MinD density over a 350 second
interval in the stadium A cell.  There is one frame for every half
second of simulation time. Above are results from the stochastic model
and below are results from the deterministic model.  The density shown
is integrated over the direction normal to the screen, so that the
data is shown in molecules/$\micron^2$.

\section*{Supplementary Information 5}
Movie that shows the evolution of MinD density over a 350 second
interval in the stadium B cell.  There is one frame for every half
second of simulation time. Above are results from the stochastic model
and below are results from the deterministic model.  The density shown
is integrated over the direction normal to the screen, so that the
data is shown in molecules/$\micron^2$.
